### 2021-03-03 paper1/paper1.tex
Fix bold math

\section{Target labels for tuning group fairness}
We will start by describing several notions of group fairness.
For each individual, we have a vector of non-sensitive attributes $x\in\mathcal{X}$, a class label $y\in\mathcal{Y}$, and a sensitive attribute $s\in\mathcal{S}$ (e.g.\ racial origin or gender).
%
We focus on the case where $s$ and $y$ are binary. 
%
We assume that a positive label $y=1$ corresponds to a positive outcome for an individual -- for example, being accepted for a loan.
%
%
\emph{Group fairness} balances a certain condition between groups of individuals with different sensitive attribute, $s$ versus $s\sp{\prime}$. 
%
The term $\hat{y}$ below is the prediction of a machine learning model that,
in most works, uses only non-sensitive attributes $x$.
%
Several group fairness criteria have been proposed (e.g. \cite{zafar2017fairnesstreatment,chouldechova2017fair,hardt2016equality}):
\begin{align}
& \text{equality of positive rate (Demographic Parity):}\nonumber\\
& \text{Pr}(\hat{y}=1|s)=\text{Pr}(\hat{y}=1|s\sp{\prime}) \label{eq:eq_dem_par}\\
& \text{equality of accuracy:}\nonumber\\
& \text{Pr}(\hat{y}=y|s)=\text{Pr}(\hat{y}=y|s\sp{\prime}) \\
& \text{equality of true positive rate (Equality of Opportunity):} \nonumber\\
& \text{Pr}(\hat{y}=1|s,y=1)=\text{Pr}(\hat{y}=1|s\sp{\prime},y=1)  \label{eq:eq_opp_cri}~.
\end{align}
\emph{Equalised odds} criterion corresponds to Equality of Opportunity (\ref{eq:eq_opp_cri}) plus equality of false positive rate.

>>>>

\section{Target labels for tuning group fairness}
We will start by describing several notions of group fairness.
For each individual, we have a vector of non-sensitive attributes $x\in\mathcal{X}$, a class label $y\in\mathcal{Y}$, and a sensitive attribute $s\in\mathcal{S}$ (e.g.\ racial origin or gender).
%
We focus on the case where $s$ and $y$ are binary. 
%
We assume that a positive label $y=1$ corresponds to a positive outcome for an individual -- for example, being accepted for a loan.
%
%
\emph{Group fairness} balances a certain condition between groups of individuals with different sensitive attribute, $s$ versus $s\sp{\prime}$. 
%
The term $\hat{y}$ below is the prediction of a machine learning model that,
in most works, uses only non-sensitive attributes $x$.
%
Several group fairness criteria have been proposed (e.g. \cite{zafar2017fairnesstreatment,chouldechova2017fair,hardt2016equality}):
\begin{align}
& \text{equality of positive rate (Demographic Parity):}\nonumber\\
& P(\hat{y}=1|s)=P(\hat{y}=1|s\sp{\prime}) \label{eq:eq_dem_par}\\
& \text{equality of accuracy:}\nonumber\\
& P(\hat{y}=y|s)=P(\hat{y}=y|s\sp{\prime}) \\
& \text{equality of true positive rate (Equality of Opportunity):} \nonumber\\
& P(\hat{y}=1|s,y=1)=P(\hat{y}=1|s\sp{\prime},y=1)  \label{eq:eq_opp_cri}~.
\end{align}
\emph{Equalised odds} criterion corresponds to Equality of Opportunity (\ref{eq:eq_opp_cri}) plus equality of false positive rate.
